Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-03-11 docs/manuscript/manuscript.tex

We also used World Bank's database to gain additional explanatory variable data for this study. World Bank (WB) provides over 200,000 published documents to understand the development policies and programs globally. Their reports, working papers, documents, and primary data are free to the public. WB DataBank is an analysis and visualization instrument that contains examples of time series data on many topics. We generated tables to analyze them by R.  We used World Development Indicators (WDI) within the DataBank is the primary World Bank collection of development indicators, organized from officially-recognized international sources. It exhibits the most current, accurate global development, and available data includes national, regional, and global estimates. We collected the 2018 surveys for the 73 countries for the following variables mentioned in \autoref{tab:summary-var}.

@@

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Notes \\\midrule
 \texttt{bicy} & Bicycle
 & DHS Program Surveys
\\\midrule
 \texttt{acar} & Animal drawn cart
 & DHS Program Surveys
\\\midrule
 \texttt{mcyc} & Motorcycle
 & DHS Program Surveys
\\\midrule
 \texttt{pcar} & Private car
 & DHS Program Surveys
\\\midrule
 \texttt{cgdp} & GDP (current US \$) 
 & World Bank Data [NY.GDP.MKTP.CD]
\\\midrule
 \texttt{tpop} & Total Population
 & World Bank Data   [SP.POP.TOTL]
\\\midrule
 \texttt{upop} & Urban population 
 & World Bank Data  (\% of total population)  [SP.URB.TOTL.IN.ZS]
\\\midrule
 \texttt{popd} & Population density 
 & World Bank Data  (people per sq. km of land area)  [EN.POP.DNST]
\\\midrule
 \texttt{land} & Land area 
 & World Bank Data  (sq. km) [AG.LND.TOTL.K2]
\\\midrule
 \texttt{lita} & Literacy rate, adult total 
 & World Bank Data  (\% of people ages 15 and above) [SE.ADT.LITR.ZS]
\\\midrule
 \texttt{lity} & Literacy rate, youth 
 & World Bank Data  (ages 15-24), gender parity index (GPI) [SE.ADT.1524.LT.FM.ZS]
\\\midrule
 \texttt{mori} & Mortality rate, under-5 
 & World Bank Data  (per 1,000 live births) [SH.DYN.MORT]
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country (DHS Program).

@@

>>>>

We also used World Bank's database to gain additional explanatory variable data for this study. World Bank (WB) provides over 200,000 published documents to understand the development policies and programs globally. Their reports, working papers, documents, and primary data are free to the public. WB DataBank is an analysis and visualization instrument that contains examples of time series data on many topics. We generated tables to analyze them by R.  We used World Development Indicators (WDI) within the DataBank is the primary World Bank collection of development indicators, organized from officially-recognized international sources. It exhibits the most current, accurate global development, and available data includes national, regional, and global estimates. We collected the most data available year (2018 and 2014) surveys for the 73 countries for the following variables mentioned in \autoref{tab:summary-var}.

@@

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Notes \\\midrule
 \texttt{bicy} & Bicycle
 & DHS Program Surveys
\\\midrule
 \texttt{acar} & Animal drawn cart
 & DHS Program Surveys
\\\midrule
 \texttt{mcyc} & Motorcycle
 & DHS Program Surveys
\\\midrule
 \texttt{pcar} & Private car
 & DHS Program Surveys
\\\midrule
 \texttt{cgdp} & GDP (current US \$) 
 & World Bank Data [NY.GDP.MKTP.CD]
\\\midrule
 \texttt{tpop} & Total Population
 & World Bank Data   [SP.POP.TOTL]
\\\midrule
 \texttt{upop} & Urban population 
 & World Bank Data  (\% of total population)  [SP.URB.TOTL.IN.ZS]
\\\midrule
 \texttt{popd} & Population density 
 & World Bank Data  (people per sq. km of land area)  [EN.POP.DNST]
\\\midrule
 \texttt{land} & Land area 
 & World Bank Data  (sq. km) [AG.LND.TOTL.K2]
\\\midrule
 \texttt{lita} & Literacy rate, adult total 
 & World Bank Data  (\% of people ages 15 and above) [SE.ADT.LITR.ZS]
\\\midrule
 \texttt{lity} & Literacy rate, youth 
 & World Bank Data  (ages 15-24), gender parity index (GPI) [SE.ADT.1524.LT.FM.ZS]
\\\midrule
 \texttt{mori} & Mortality rate, under-5 
 & World Bank Data  (per 1,000 live births) [SH.DYN.MORT]
\\\midrule
 \texttt{prec} & Average precipitation in depth (mm per year)
 & World Bank Data  Average precipitation in depth (mm per year)
 [AG.LND.PRCP.MM]
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country (DHS Program).

@@

\subsection{Factor Analysis}
